Growth Resilience

### 2017-09-15 analysis/analysis_resilience_bai.Rmd
update tables mhuber

letraArt <- cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraArt #Manual (IMPROVE IT)
letraArt <- data.frame(Group = as.factor(c('25', '212')),
                     Letter = as.factor(c('a','a')),
                     MonoLetter = as.factor(c('a','a'))) %>% mutate(var ='rt')
letraBrt <- cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraBrt
letraABrt <- cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraABrt 
```

@@

```{r}

letrasA <- rbind(letraArs, letraArc, letraArt, letraArrs) %>% 
  mutate(disturb_year = 
           case_when(Group == "25" ~ "2005",
                     Group == "212" ~ "2012")) %>% 
  dplyr::select(-Group)

letrasB <- letrasB %>% rename(site = Group)

>>>>

letraArt <- cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraArt #Manual (IMPROVE IT)
letraArt <- data.frame(Group = as.factor(c('25', '212')),
                     Letter = as.factor(c('a','a')),
                     MonoLetter = as.factor(c('a','a'))) %>% mutate(var ='rt')
letraArt 
letraBrt <- cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraBrt
letraABrt <- cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraABrt 
```

@@

```{r}
letrasA <- rbind(letraArs, letraArc, letraArt, letraArrs) %>% 
  mutate(disturb_year = 
           case_when(Group == "25" ~ "2005",
                     Group == "212" ~ "2012")) %>% 
  dplyr::select(-Group)

letrasB <- rbind(letraBrs, letraBrc, letraBrt, letraBrrs) %>% rename(site = Group)
